Studying the Performance of the Jellyfish Optimiser for the Application of Projection Pursuit

### 2024-05-31 optim.qmd
take back the print of the final dataset

@tbl-smoothness-squintability presents all the parameters calculated for smoothness and squintability, with the column "smooth" for smoothness and "theta3" for squintability. @fig-idx-proj-dist shows the relationship between the index value against the projection distance for each problem following the binning procedure. @tbl-all-sim displays the first five rows after combining all calculations.

@@

```{r}
#| label: tbl-all-sim
#| tbl-cap: The first five rows of the datasets after combining all the calculation. The smoothness and squintability variable are uniquely characterised by the index function used and the data dimension, and thus do not vary across n\\_jellies and max\\_tries. Variables I\\_max\\_max, P\\_J\\_hat, and time are calculated at each 51 observations.
load(here::here("data/sim_df.rda"))
sim_df |> 
  dplyr::select(index, d, smoothness, squintability, n_jellies, max_tries, 
                I_max_max, P_J_hat, time) |> 
  arrange(index, d, n_jellies, max_tries) |> 
  head(5) |> 
  kable(digits = 3)
```

>>>>

@tbl-smoothness-squintability presents all the parameters calculated for smoothness and squintability, with the column "smooth" for smoothness and "theta3" for squintability. @fig-idx-proj-dist shows the relationship between the index value against the projection distance for each problem following the binning procedure.

<!-- @tbl-all-sim displays the first five rows after combining all calculations.  -->

@@

```{r eval = FALSE}
#| label: tbl-all-sim
#| tbl-cap: The first five rows of the datasets after combining all the calculation. The smoothness and squintability variable are uniquely characterised by the index function used and the data dimension, and thus do not vary across n\\_jellies and max\\_tries. Variables I\\_max\\_max, P\\_J\\_hat, and time are calculated at each 51 observations.
load(here::here("data/sim_df.rda"))
sim_df |> 
  dplyr::select(index, d, smoothness, squintability, n_jellies, max_tries, 
                I_max_max, P_J_hat, time) |> 
  arrange(index, d, n_jellies, max_tries) |> 
  head(5) |> 
  kable(digits = 3)
```

### 2024-05-31 optim.tex
take back the print of the final dataset

\begin{tcolorbox}[enhanced jigsaw, colback=white, arc=.35mm, leftrule=.75mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colbacktitle=quarto-callout-note-color!10!white, bottomtitle=1mm, toptitle=1mm, opacityback=0, bottomrule=.15mm, titlerule=0mm, coltitle=black, rightrule=.15mm, breakable, toprule=.15mm, left=2mm]

@@

Table~\ref{tbl-smoothness-squintability} presents all the parameters
calculated for smoothness and squintability, with the column ``smooth''
for smoothness and ``theta3'' for squintability.
Figure~\ref{fig-idx-proj-dist} shows the relationship between the index
value against the projection distance for each problem following the
binning procedure. Table~\ref{tbl-all-sim} displays the first five rows
after combining all calculations.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0714}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0357}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1310}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1667}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0952}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1429}}@{}}

@@

\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
index
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
d
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
smoothness
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
squintability
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n\_jellies
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
max\_tries
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
I\_max\_max
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P\_J\_hat
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
time
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
MIC & 6 & 2.394 & 1.623 & 20 & 50 & 0.999 & 1.00 & 2.479 secs \\
MIC & 6 & 2.394 & 1.623 & 20 & 100 & 0.999 & 0.96 & 8.950 secs \\
MIC & 6 & 2.394 & 1.623 & 50 & 50 & 1.000 & 1.00 & 5.651 secs \\
MIC & 6 & 2.394 & 1.623 & 50 & 100 & 1.000 & 0.64 & 13.223 secs \\
MIC & 6 & 2.394 & 1.623 & 100 & 50 & 1.000 & 0.76 & 19.453 secs \\

>>>>

\begin{tcolorbox}[enhanced jigsaw, left=2mm, coltitle=black, opacitybacktitle=0.6, colback=white, breakable, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, toptitle=1mm, bottomtitle=1mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomrule=.15mm, rightrule=.15mm, opacityback=0]

@@

Table~\ref{tbl-smoothness-squintability} presents all the parameters
calculated for smoothness and squintability, with the column ``smooth''
for smoothness and ``theta3'' for squintability.
Figure~\ref{fig-idx-proj-dist} shows the relationship between the index
value against the projection distance for each problem following the
binning procedure.

@@

\begin{table}

@@

\end{table}%
